A thesis draft

### 2018-10-17 res/sections/07-Introduction.tex
Add document organization section

 This thesis is organized as follows:
 \begin{itemize}
  \item Chapter~\ref{chap:background} provides background informations about 5G 
and the technologies used to build an ETSI compliant architecture
 \end{itemize}

>>>>

 This thesis is organized as follows:
 \begin{itemize}
  \item Chapter~\ref{chap:background} describes background information about 5G 
and the technologies used to build an ETSI compliant architecture
  \item Chapter~\ref{chap:prjan} explains the analysis performed on the 
requirements provided and the design choices performed.
  \item Chapter~\ref{chap:archimpl} provides an in-depth view of the 
high-level architectural implementation.
  \item Chapter~\ref{chap:conclusions} wraps up the overall project experience.
 \end{itemize}
